\documentclass[11pt,a4paper]{article}

\usepackage[margin=2.5cm]{geometry}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning}

\title{MTG Commander Scoreboard\\[0.5em]\large Design Document}
\author{}
\date{}

% Colors
\definecolor{p1}{RGB}{228,87,46}
\definecolor{p2}{RGB}{0,115,178}
\definecolor{p3}{RGB}{76,175,80}
\definecolor{p4}{RGB}{156,39,176}

% Styles
\tikzset{
    player/.style={rectangle, draw, thick, minimum size=1.6cm, font=\bfseries, align=center},
    admin/.style={rectangle, draw, thick, minimum width=3cm, minimum height=1.2cm, font=\small, align=center},
    edge/.style={->, >={Stealth[length=2mm]}, thick, bend left=12},
    lbl/.style={font=\scriptsize, fill=white, inner sep=1pt}
}

\begin{document}
\maketitle

\section{Introduction}

Magic: The Gathering is a trading card game. \textbf{Commander} is a multiplayer format typically played with 4 players, each starting at 40 life. Players also track \emph{commander damage}---if you take 21 damage from any single opponent's commander, you lose.

This document describes a dedicated scoreboard: a device placed in the center of the table with four screens arranged in a 2$\times$2 grid, one facing each player.

\section{Requirements}

The device must:

\begin{enumerate}
    \item \textbf{Track life totals} --- one value per player ($n$ values)
    \item \textbf{Track commander damage} --- one value per ordered pair of players ($n \times (n-1)$ values)
    \item \textbf{Provide an admin panel} --- reset game, configure player count and starting life
\end{enumerate}

\subsection{Life Totals}

\begin{center}
\begin{tikzpicture}
    \node[player, fill=p1!20] (P1) at (0, 1.8) {P1\\40};
    \node[player, fill=p2!20] (P2) at (2.2, 1.8) {P2\\40};
    \node[player, fill=p3!20] (P3) at (0, 0) {P3\\40};
    \node[player, fill=p4!20] (P4) at (2.2, 0) {P4\\40};
\end{tikzpicture}
\end{center}

\subsection{Commander Damage}

\begin{center}
\begin{tikzpicture}
    \node[player, fill=p1!20] (P1) at (0, 2) {P1\\37};
    \node[player, fill=p2!20] (P2) at (3, 2) {P2\\31};
    \node[player, fill=p3!20] (P3) at (0, 0) {P3\\40};
    \node[player, fill=p4!20] (P4) at (3, 0) {P4\\19};

    \draw[edge, p1] (P1) to node[lbl] {7} (P2);
    \draw[edge, p2] (P2) to node[lbl] {3} (P1);
    \draw[edge, p1] (P1) to node[lbl, pos=0.3] {15} (P4);
    \draw[edge, p4] (P4) to node[lbl, pos=0.7] {6} (P1);
    \draw[edge, p2] (P2) to node[lbl] {9} (P4);
    \draw[edge, p3] (P3) to node[lbl] {11} (P4);
\end{tikzpicture}
\end{center}

For 4 players: $4 \times 3 = 12$ directed values to track.

\subsection{Admin Panel}

\begin{center}
\begin{tikzpicture}
    \node[admin, fill=gray!10] (admin) {New Game\\Player Count\\Starting Life};
\end{tikzpicture}
\end{center}

Accessed via hidden menu (e.g., hold button) or dedicated interface.

\section{Design Constraints}

\subsection{How do players adjust values?}

Life totals are simple: each player adjusts their own screen. Input must be \textbf{local}---no passing devices.

Commander damage is harder. It requires specifying \emph{source}, \emph{target}, and \emph{amount}. Options:
\begin{itemize}
    \item Source-initiated: attacker selects target, enters damage
    \item Target-initiated: damaged player selects source, enters damage received
    \item Modal: switch between ``life mode'' and ``commander damage mode''
\end{itemize}

\subsection{How do we display commander damage?}

Showing 12 values on 4 screens is cluttered. Options:
\begin{itemize}
    \item Per-player view: each screen shows only that player's 3 incoming values
    \item On-demand: hidden by default, shown when needed
    \item Central display: a fifth screen or overlay shows the full graph
\end{itemize}

\subsection{Complexity Summary}

\begin{center}
\begin{tabular}{lcc}
\hline
\textbf{Feature} & \textbf{Values} & \textbf{Difficulty} \\
\hline
Life totals & $n$ & Simple \\
Commander damage & $n(n-1)$ & Hard \\
\hline
\end{tabular}
\end{center}

\end{document}
